The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-22 project/paper/output.tex
Tweaks to properties.

\section{The Skew-Normal}
\label{sec:properties}

@@

\subsection{Basics}

@@

which is the pdf of the normal distribution. Furthermore, when $\lambda > 0$,
the curve skews to the left, and when $\lambda < 0$, it skews to the right (a
property we will prove in section \ref{subsec:four-properties}).

\subsection{Four Properties}
\label{subsec:four-properties}

The following four properties of the skew-normal, given by \citet{main}, help
shed light on our enigmatic new distribution:

@@

\begin{proof}
  To prove our result, we make use of Lemma 1 in \citet{azzalini}, which we
  restate here:

@@

  This lemma provides a very useful corollary:

@@

  which is the MGF of the $\chi^2_1$. Since $Z$ is equal in distribution to
  $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}

@@

  On $A_1$: $y = -x \Ra x = -y$ and $\J = \left| \frac{dx}{dy} \right| = |-1|
  = 1$, yielding

@@

  Similarly, on $A_2$: $y = x \Ra x = y$ and $\J = \left| \frac{dx}{dy}
  \right| = |1| = 1$, yielding

@@

  On $A_3$, we have $x = 0 \Ra y = 0$ and $\J = \left| \frac{dx}{dy} \right| =
  |0| = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.

@@

\begin{property} \label{prop:4}
  The MGF of $SN(0,1,\lambda)$ is

@@

\begin{proof}
  According to Equation 5 in \citet{azzalini}, the MGF of $SN(\mu, \sigma,
  \lambda)$ is

@@

  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}} \in (-1, 1)$. It follows
  that the MGF of the $SN(0, 1, \lambda)$ is

>>>>

\section{The Skew-Normal Distribution}
\label{sec:properties}

@@

\subsection{Foundations}

@@

which is the pdf of the normal distribution ($\mu$, $\sigma$). Furthermore,
when $\lambda > 0$, the curve skews to the left, and when $\lambda < 0$, it
skews to the right (a property we will prove in section
\ref{subsec:four-properties}).

\subsection{Properties of the Standard Skew-Normal Distribution}
\label{subsec:four-properties}

The following four properties of the standard skew-normal, given by
\citet{main}, help shed light on our enigmatic new distribution:

@@

\begin{proof}
  To prove our result, we begin by examining Lemma 1 in \citet{azzalini}, which
  we restate here:

@@

  This lemma is extended by a corollary which gives a very helpful result for
  the above defined $f_0$ and $f$:

@@

  which is the mgf of the $\chi^2_1$. Since $Z$ is equal in distribution to
  $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}

@@

  On $A_1$: $y = -x \Ra x = -y$ and the Jacobian $\J = \left| \frac{dx}{dy}
  \right| = |-1| = 1$, yielding

@@

  Similarly, on $A_2$: $y = x \Ra x = y$ and the Jacobian $\J = \left|
  \frac{dx}{dy} \right| = |1| = 1$, yielding

@@

  On $A_3$, we have $x = 0 \Ra y = 0$ and Jacobian $\J = \left| \frac{dx}{dy}
  \right| = |0| = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.

@@

\begin{property} \label{prop:4}
  The moment generating function of $SN(0,1,\lambda)$ is

@@

\begin{proof}
  According to Equation 5 in \citet{azzalini}, the mgf of $SN(\mu, \sigma,
  \lambda)$ is

@@

  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}} \in (-1, 1)$. It follows
  that the mgf of the $SN(0, 1, \lambda)$ is
